Project 1 FYS-STK3155

### 2022-09-08 doc/project1.tex

\end{document}

>>>>

Proof of $var(\beta) = \sigma^{2}(X^{T}X)^{-1}$
$$var(\beta) = var((X^{T}X)^{-1}X^{T}y)$$
Because we are assuming $(X^{T}X)^{-1}X^{T}$ to be deterministic and $y$ to be stochastic, we can rewrite the $var(\beta)$ as following:
$$var(\beta) = (X^{T}X)^{-1}X^{T}var(y)((X^{T}X)^{-1}X^{T})^{T}$$
$$ = (X^{T}X)^{-1}X^{T}var(y)(X^{T})^{T}((X^{T}X)^{-1})^{T}$$
Since $(X^{T})^{T} = X$ and $(X^{T}X)^{-1})^{T}$ = $(X^{T}X)^{T})^{-1} = (X^{T}X)^{-1}$
$$ = (X^{T}X)^{-1}X^{T}var(y)X(X^{T}X)^{-1} $$
We know var(y) = $\sigma^{2}$, and since it is a scalar it is commutative. Thus we may move it freely
$$ = \sigma^{2}(X^{T}X)^{-1}X^{T}X(X^{T}X)^{-1} $$
$$ = \sigma^{2}(X^{T}X)^{-1} $$
$\blacksquare$
\end{document}
